Upgrades to the SINQ Cold Neutron Source

### 2015-09-16 paper.tex
last revisions for now

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.38,trim={1cm 2.35cm 1cm 0cm},clip]{graphics/parametric_REH.pdf}
\end{center}
\caption{\label{parametric_REH}The envelope formed by the spectra from all 176 cases considered (upper) and their figures of merit (lower) which is total current from 3 to 6 \AA{}.}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.26,trim={0cm 0cm 0cm 0cm},clip]{graphics/parametric_REH.pdf}
\end{center}
\caption{\label{parametric_REH}The envelope formed by the spectra from all 176 cases considered (upper) and their figures of merit (lower) which is total current from 3 to 6 \AA{}.  Case000 is the case with the REH completely filled.}
\end{figure}

@@
